Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-12 rates-neurips-21/rates.tex
typo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Rate Transfers with Polyhedral Surrogate Losses}

% \And separates authors; \AND separates with forced line break
\author{%
  Rafael Frongillo \\
  U. Colorado, Boulder \\
  \texttt{raf@colorado.edu} \\
  \And
  Bo Waggoner \\
  U. Colorado, Boulder \\
  \texttt{bwag@colorado.edu}
}

@@

\begin{definition}[Rate Transfer]\label{def:transfer}
  A function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$ is called a \emph{rate transfer function.}
	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$, we say $(L,\psi)$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
  \begin{equation}
    \label{eq:conditional-transfer}
    \forall p\in\simplex, \forall u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~.
  \end{equation}
  We say $(L,\psi)$ satisfy a \emph{rate transfer} of $\zeta$ for $\ell$ if
  \begin{equation}
    \label{eq:transfer}
    \forall \D, \forall h, \quad R_\ell(\psi \circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
  \end{equation}
\end{definition}
In particular, we say $(L,\psi)$ satisfy a \emph{linear} rate transfer for $\ell$ if $\zeta(t) \leq Ct$ for some $C > 0$.
Such a transfer implies $R_{\ell}(\psi \circ h;\D) \leq C R_L(h;\D)$, i.e. the convergence rate of a surrogate learning problem transfers directly to the target problem.
This appears to us to be the best one can hope for, except perhaps for some strange artificial construction.

@@

% Acknowledgements (automatically hidden in submission)
%\begin{ack}
%
%\end{ack}

@@

\bibliography{references}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Rate Transfers with Polyhedral Surrogate Losses /\\
  Surrogate Regret Bounds for Polyhedral Losses}
% \And separates authors; \AND separates with forced line break
\author{%
  Rafael Frongillo \\
  U. Colorado, Boulder \\
  \texttt{raf@colorado.edu} \\
  \And
  Bo Waggoner \\
  U. Colorado, Boulder \\
  \texttt{bwag@colorado.edu}
}

@@

\begin{definition}[Rate Transfer]\label{def:transfer}
  A function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$ is called a \emph{rate transfer function.}
	Given a target $\ell:\R\to\reals^\Y$ and rate transfer function $\zeta$, we say surrogate $L:\reals^d\to\reals^\Y$ and link $\psi : \reals^d \to \R$ satisfy a \emph{conditional rate transfer} of $\zeta$ for $\ell$ if
  \begin{equation}
    \label{eq:conditional-transfer}
    \forall p\in\simplex, \forall u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~.
  \end{equation}
  We say $(L,\psi)$ satisfy a \emph{rate transfer} of $\zeta$ for $\ell$ if
  \begin{equation}
    \label{eq:transfer}
    \forall \D, \forall h, \quad R_\ell(\psi \circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
  \end{equation}
\end{definition}
In particular, we say $(L,\psi)$ satisfy a \emph{linear} rate transfer for $\ell$ if $\zeta(t) \leq Ct$ for some $C > 0$.
Such a transfer implies $R_{\ell}(\psi \circ h;\D) \leq C R_L(h;\D)$, i.e. the convergence rate of a surrogate learning problem transfers directly to the target problem.
This appears to us to be the best one can hope for, except perhaps for some strange artificial construction.

@@

% Acknowledgements (automatically hidden in submission)
\begin{ack}
  \raf{Stephen Becker for help with the strong convexity stuff}
  \raf{Nishant Mehta for many discussions}
  \raf{Jessie Finocchiaro for discussions}
\end{ack}

@@

\bibliographystyle{plainnat}
\bibliography{diss,extra}
